    
\cvsection{Professional Experience}

\cvevent{Product Consultant}{Juniper Networks}{September 2021--Current}{New Haven, Connecticut}
\begin{itemize}
    \item Scripted a dynamic inventory plugin for Ansible using Paragon Automation Suite as the source of truth
    \item Implemented a Zero touch provisioning system using flask (Python) and Kea DHCP server to provision hundreds of Juniper devices based on a single source of truth. This led to a 1500\% decrease in required engineering resources and a 400\% decrease in provisioning time.
    \item Validated the design submitted by the design team for a 911 network which carried mission critical traffic.
    \item Attended regular security briefings to decide if a security issue applied to the current project
    \item Designed Method of Procedure documents for various phases of the project 
    \item  Used Python to automate provisioning of configuration for a datacenter based on Juniper Apstra with minimal downtime
    \item Participated in on-call rotations to assist with a datacenter migration with minimal disruption to production traffic.
    \item Used Apstra's telemetry tools to investigate and troubleshoot anomalies in an L3 fabric network
    
    \item Stack: \cvtag{Python} \cvtag{Flask} \cvtag{Kea DHCP server} \cvtag{Juniper Apstra}
\end{itemize}

\divider

\cvevent{Full Stack developer}{ING}{March 2021--December 2021}{San Francisco, California}
\begin{itemize}
    \item Implemented features in the company's flagship app using React Native
    \item Built REST APIs using Google Cloud functions which are consumed by the app
    \item Architected sequence diagrams for the design of the app using Miro
    \item Built a location based search engine using a custom built implementation of Geohashes and programmed a search filter using Dice's Coefficient
    \item Wrote Unit tests using Mocha to verify and validate functionality
    \item Participated in an agile development environment and used Jira to keep track of user stories and tickets
    \item Stack: \cvtag{React Native} \cvtag{Firebase} \cvtag{Google Cloud functions} \cvtag{Node.js} \cvtag{JavaScript} \cvtag{Miro} \cvtag{Jira}
\end{itemize}
\divider

\cvevent{Network and System Administrator (Freelance)}{Pat \& Venky}{January 2018--Current}{Chennai, India}
\begin{itemize}
    \item Decommissioned an aging Windows based fileshare system and deployed a high availability NAS setup which drastically improved uptime and provided disaster recovery options.
    \item Configured fileshares with access based controls preventing unauthorized access to proprietary business data.
    \item Deployed a Unifi network to ensure greater network reliability and create network segmentation policies.
   \end{itemize}
\divider


\cvevent{Research Assistant}{University of Nevada at Las Vegas}{June 2020--August 2020}{Las Vegas, Nevada}
\begin{itemize}
    \item Collaborated with Dr. Yoohwan Kim and Dr. Ju-Yeon Jo in researching the effectiveness of Multipath TCP in improving TCP throughput.
    \item Deployed network simulations to measure the throughput under varying latency and loss rate for Singlepath and Multipath TCP networks.
    \item Processed the output of iperf3's JSON results and graphed the data to visualize trends in throughput.
    \item Stack: \cvtag{Python} \cvtag{Mininet} \cvtag{Plotly} \cvtag{pandas}
\end{itemize}
\divider


