\cvsection{Projects}

\href{https://rsun.dev}{Website Portfolio}
\begin{itemize}
    \item Built a personal website using Gatsby with CI/CD on Netlify.
    \item The PDF resume on the site is written in \LaTeX{} and generated with GitHub actions
    \item The website automatically integrates the latest version of the resume whenever a commit is made to the \LaTeX{} repository.
\end{itemize}
    
\href{https://github.com/ngrover2/teammaking}{Teammaking}
\begin{itemize}
    \item Developed a full stack application that generates teams based on a survey.
    \item Incrementally built using React, Node and using mySQL following an agile development methodology.
\end{itemize}


\href{https://github.com/networking-discord/network-ranger}{Network ranger}
\begin{itemize}
    \item Refactored the code base and code reviewed a Discord bot that manages user roles and permissions in a discord server.
    \item Optimized  a docker workflow to prevent a security breach.
\end{itemize}
    
\href{https://github.com/rahul-sundaresan/network-gui/}{Network-gui}
\begin{itemize}
    \item Created a React app queries a SDN switch and uses react-d3-graph to graph the topology of the network.
\end{itemize}


\href{https://github.com/rahul-sundaresan/ccn-6166-p2}{TCP over UDP}
\begin{itemize}
    \item Implemented the TCP go-back-N and selective repeat protocols over UDP.
    \item  A toy project written in python to better understand the implementation of TCP.
\end{itemize}


\href{https://github.com/rahul-sundaresan/6166-project-1}{Tiny HTTP system}
\begin{itemize}
    \item Implemented a very basic HTTP client and server in less than 100 LoC combined which supports PUT and POST requests with file transfer.
\end{itemize}


\href{https://github.com/rahul-sundaresan/agency-spotter-scraper}{Agency spotter scraper}
\begin{itemize}
    \item Designed a pipeline to scrape the agency spotter website using Python's Beautiful Soup library and a bash script.
\end{itemize}

